---
title: "HW08, pt 2: Exploring NYT API"
author: "Julia Du"
date: "`r lubridate::today()`"
output: 
  github_document:
    toc: true
---

**Note:** You're going to need to register for a NYT Developer account in order to use their APIs, all of which require authentication. Before running the code you see below, you'll need to open your .Rprofile with `file.edit(here::here(".Rprofile"))` and add your NYT API key to the .Rprofile with `options(nyt_semantics_key = "my_user_name")`.

## Load necessary libraries

```{r, message = FALSE}
library(tidyverse)
library(stringr)
library(jsonlite)
library(httr)
library(lubridate)
library(viridis)

nyt_key <- getOption("nyt_semantics_key")

theme_set(theme_minimal())
```

# Overview

The goal here was to look at how coverage of President Obama on gay marriage fluctuated with time. I used the New York Times's Article Search API and heavily relied upon their [documentation](https://developer.nytimes.com/docs/articlesearch-product/1/routes/articlesearch.json/get) to figure out how to format my request. I also drew heavily from [this site](https://plsc-31101.github.io/course/collecting-data-from-the-web.html#writing-api-queries).

## Using API for 1 pg of results
```{r nyt_nerd}
base.url <- "https://api.nytimes.com/svc/search/v2/articlesearch.json"
search_term <- "Obama gay marriage"
filter_query <- 'source:("The New York Times") AND news_desk:("National") 
AND section_name:("U.S.") AND document_type:("article")' 
begin <- "20090120" #Obama presidency start
end <- "20170120" #Obama presidency end

articles <- GET(base.url, 
                query = list(`q` = search_term,
                             `fq` = filter_query,
                             `begin_date` = begin,
                             `end_date` = end,
                             `api-key` = nyt_key))

response <- content(articles, "text")

response_df <- fromJSON(response, simplifyDataFrame = TRUE, flatten = TRUE) 

docs <- response_df %>%
  with(response) # tidyverse alternative to response_df$response$docs

#extract total hits
hits <- response_df %>%
  with(hits) # tidyverse alternative to response_df$response$meta$hits

# get number of pages
pages <- ceiling(hits/10)

```


## Iterating API use 
```{r iterate_nyt, cache = TRUE}
nyt_api <- function(term, pg){
  base.url <- "https://api.nytimes.com/svc/search/v2/articlesearch.json"
  filter_query <- 'source:("The New York Times") AND news_desk:("National") AND section_name:("U.S.") AND document_type:("article")'
  begin <- "20090120" #Obama term start
  end <- "20170120" #Obama term end
  
  # send GET request
  articles <- GET(base.url, 
                  query = list(`q` = term,
                               `fq` = filter_query,
                               `begin_date` = begin,
                               `end_date` = end,
                               `page` = pg,
                               `api-key` = nyt_key))
  
  # Parse response to JSON
  response <- content(articles, "text")
  
  response_df <- fromJSON(response, simplifyDataFrame = TRUE, flatten = TRUE) 

  message(glue("Scraping page {pg}"))
  
  response_df %>%
    with(response)
}

#nyt_api(term = "gay marriage", pg = 4)

nyt_api_slow <- slowly(nyt_api, rate = rate_delay(2))

docs_df <- map_dfr((0:pages), ~nyt_api_slow(term = "Obama gay marriage", pg = .))
```



# Visualizing NYT coverage
```{r viz_nyt}
date_docs <- docs_df %>%
  mutate(date = ymd_hms(pub_date), .before = abstract) %>% 
  count(floor_date(date, "month")) %>%
  rename(month = 1, count = n) %>%
  mutate(year = year(month), year = as.factor(year))

date_docs %>%
  ggplot(aes(x = month, y = count, fill = year)) +
  geom_col() +
  labs(title = "NYT monthly coverage of President Obama on gay marriage", subtitle = "From Jan. 2009 to Jan. 2017", x = "Date", y = "Number of articles", fill = "Year", caption = "Source: nytimes.com") +
  theme(axis.text.x = element_blank()) 
```

There are several notable peaks in coverage, namely mid-2009, early/mid-2012, mid-2013, and mid-2015. 

In June 2009, Obama signed a [Presidential Memo](https://www.pbs.org/wgbh/americanexperience/features/stonewall-milestones-american-gay-rights-movement/) that let same-sex partners of federal employees receive specified benefits. 
There were a lot of articles in early/mid-2012, likely because it was an election year and gay marriage was one of the main issues presidential candidates were evaluated on. I'm not too sure why there was a peak in mid-2013, but the peak in 2015 was due to the historic Supreme Court decision that declared gay marriage legal in the U.S. 

