---
title: "HW08, pt 2:"
author: "Julia Du"
date: "`r lubridate::today()`"
output: 
  github_document:
    toc: true
---

## Load necessary libraries

```{r, message = FALSE}
library(tidyverse)
library(stringr)
library(jsonlite)
library(httr)

nyt_api <- getOption("nyt_semantics_key")
guardian_api <- getOption("guardian_key")

theme_set(theme_minimal())
```

keep in mind you'll need to have your own API key for both NYT (Semantics API) & Guardian API. store it in .Rprofile w/ format of options(keyname = "actualkeycode").

## Overview
compare coverage of BLM this past yr geographically?

track coverage of gay marriage over time? since maybe 2000?

```{r}
guard_equal <- GET(
  url = "https://content.guardianapis.com/tags?",
  query = list(q = "equal-marriage",
               format = "xml",
               api_key = "guardian_api"))

```

## 

```{r}

```


```{r}

```


```{r}

```


```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
